---
title: "anony_implementation"
author: "Yong Cha"
## modified by jmbatto
output: 
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: true
    
---


# Package Loading
```{r package, message=FALSE}
require(devtools)
install_github('jmbatto/entroPD')
require(entroPD)
```



# Implementation

## Data Import
```{r load, echo=FALSE}
## load('./data/data_adult.Rdata')
load(url("https://github.com/jmbatto/entroPD/blob/master/data/data_adult.RData?raw=true"))
```

```{r data}
str(adult)
```


## Partition Data

### Define Attributes

* Defines the properties of variables to partition data 
    * __Attributes (or Identifier)__ : (Definite) identifier 
        * SSN, Address, Name, etc...
    * __Target Attributes (TA)__ : Target variable corresponding to the response variable when analyzing  
    * __Quasi-Identifiers (QI)__ : Unclear identifier 
        * zip code, birthdate, gender, etc...
    * __Sensitive Attirbutes (SA)__ : Personal sensitive information 
        * Disease, disease information, annual salary, etc... 
    * __Insensitive Attributes (IS)__ : Other non-sensitive information 
    

```{r part}
# TA (Target)
TA <- c('income')
# QI (Quasi-Identifiers)
QI <- c('age', 'workclass', 'education', 'marital.status', 'occupation', 'race', 'sex', 'native.country')
#QI <- c('age', 'workclass', 'education', 'marital.status')
# SA (Sensitive Attributes)
SA <- c('capital.gain', 'capital.loss')
# IS (Insensitive)
IS <- c('relationship', 'hours.per.week', 'education.num')
# Remove
RM <- c('fnlwgt')
```

### `parda` Function application 

```{r parda}
adult.QI <- parda(adult, QI, TA)
str(adult.QI)
```



## `cpselec` Function application 

```{r cpselec}
cp.val <- cpselec(10, 100, 2)
cp.val
```



## `rpaclass` Function application 


### `lapply` eval

```{r rpal}
cp.res.la <- rpaclass(adult.QI, cp.val, matrix(c(0,1,2,0), ncol=2), cval = 100)
cp.res.la[[1]]
```


## `lanode` Function application 

```{r lanode}
node.res <- lanode(cp.res.la)
node.res[[30]]
```


## `qigrp` Function application 

```{r qigrp, results='asis'}
qigrp.res <- qigrp(adult.QI, node.res, mcs=8)
knitr::kable(head(qigrp.res[[30]], 20))
```


## `eclass` Function application 

```{r eclass, results='asis'}
equiclass <- eclass(qigrp.res, QI, TA)
knitr::kable(head(equiclass[[30]], 20))
```



## `resume` Function application 

```{r resume, results='asis'}
measure.res <- resume(equiclass, kanon = 5, maxsup = 0.01)
knitr::kable(head(measure.res, 20))
```


## `plot.resume` Function application 
```{r plot, message=FALSE, fig.align='center', fig.height=7, fig.width=11, fig.cap='Figure 1'}
plot(measure.res)
```
